Gsmodutils: A python based framework for test driven genome scale metabolic model development

### 2017-12-20 article/article.tex
Article additions

\subsection{Evaluation of model validation criteria}
Several crucial validation criteria were identified from the experimental and theoretical analysis of the models found in the original publications.
We note that this is not an exhaustive set of criteria.
This section is designed to serve as a use case for the gsmodutils framework, not to comprehensively review the initial publications.
\\
\textbf{TCA cycle}\\
\textbf{Proton balanced results}\\
\textbf{Predictions of knockouts}\\
\textbf{Flux validation against 13C data}\\
\textbf{Under acidogenic stress (H inhibited conditions) } \\
\textbf{Solvent formation Cell recycling in solventogenic phase}\\

% Conclusions
\subsection{Remarks} 
\textbf{To fill in when validation is complete.}

>>>>

\subsection{Evaluation of model validation criteria}
Several crucial validation criteria were identified from the experimental and theoretical analysis of the models found in the original publications.
We note that this is not an exhaustive set of criteria.
This section is designed to serve as a use case for the gsmodutils framework, not to comprehensively review the initial publications.
\\

\textbf{TCA cycle}\\
\textbf{Proton balanced results}\\
\textbf{Predictions of knockouts}\\
The inital publication for iCAC802 included validation of four gene knockout mutant strains.
$\Delta ack$ acetate kinase.\\
$\Delta ptb$ phosphotransbutrylase.\\
$\Delta adc$ acetoacetate decarboxylase. \textbf{This reaction is present and the knock out works as expected but not annotated correctly.}\\
$\Delta hdb$ hydroxybutyryl-CoA dehydrogenase. \\

\textbf{Flux validation against 13C data}\\
\textbf{Under acidogenic stress (H inhibited conditions) } \\
\textbf{Solvent formation Cell recycling in solventogenic phase}\\

% Discuss these results
\subsection{Remarks} 
Reproducing the results of the initial publication of the iCAC802 model \cite{dash2014capturing} was possible.
However, it is notworthy to point out that there were a number of inconsistencies between the annotation in the published model and the publication.
Notably, the gene ``adc'', which codes for acetoacetate decarboxylase was missing from the initial annotation.
We would stress that these did not significantly impact the results of the model or the claims made in the publication.
